biclaR: Estimating the socio-environmental impacts of car substitution by bicycle and public transit using open tools

### 2023-12-21 paper/PaperTRA/PaperTRA_rev1.tex
shorter aknowlegments

The intermodality scenario considers trips combining PT and cycling for
the first and last legs. In a conservative approach, we have restricted
our analysis to the first and last legs with a combined length of up to
5 km (for instance: 1 km from origin to interface A plus 4 km from
interface B to destination) or up to 25 minutes on bike. Furthermore, we
have imposed restrictions on PT usage to include only trips with no PT
transfers, and up to 2 hours (120 min). Additionally, we have only
included PT modes that can easily accommodate bicycles, such as trains,
ferries, trams, and inter-municipal bus lines equipped with bike racks
(Figure \ref{fig:map1}). Figure \ref{fig:map2} illustrates the resulting
bicycle routes to access the main PT interfaces in the LMA.

@@

This research was funded by the Lisbon's Metropolitan Department of
Transport (TML - Transportes Metropolitanos de Lisboa, E.M.T., S.A.),
under the \emph{biclaR} Project. This work is part of the research
activity carried out at Civil Engineering Research and Innovation for
Sustainability (CERIS) and has been funded by Fundação para a Ciência e
a Tecnologia (FCT), Portugal in the framework of project
UIDB/04625/2020. The authors thank Thomas Götschi (HEAT for Cycling) for
providing access to HaaS tool, which is under development.

>>>>

The intermodality scenario considers trips combining PT and cycling for
the first and last legs. In a conservative approach, we have restricted
our analysis to the first and last legs with a combined length of up to
5 km (for instance: 1 km from origin to interface \emph{A} plus 4 km
from interface \emph{B} to destination) or up to 25 minutes on bike.
Furthermore, we have imposed restrictions on PT usage to include only
trips with no PT transfers, and up to 2 hours (120 min). Additionally,
we have only included PT modes that can easily accommodate bicycles,
such as trains, ferries, trams, and inter-municipal bus lines equipped
with bike racks (Figure \ref{fig:map1}). Figure \ref{fig:map2}
illustrates the resulting bicycle routes to access the main PT
interfaces in the LMA.

@@

This research was funded by the Lisbon's Metropolitan Department of
Transport (TML - Transportes Metropolitanos de Lisboa, E.M.T., S.A.),
under the \emph{biclaR} Project. This work is part of the research
activity carried out at Civil Engineering Research and Innovation for
Sustainability (CERIS) and has been funded by Fundação para a Ciência e
a Tecnologia (FCT), Portugal in the framework of project
UIDB/04625/2020.
